### 2020-06-19 article.tex
Some more recent changes

% Recycling put aside, 
Another important aspect of Krylov methods is their ability
to deal with multiple right-hand sides simultaneously. Block Krylov methods~\cite{gutknecht2006block} are
designed for solving linear systems $A X = B$, where
$X$ and $B$ are tall-and-skinny matrices with $k \geq 1$ columns. These methods are
less frequently implemented in general purpose libraries because they require
somehow more involved kernels such as matrix--matrix multiplication, instead of
matrix--vector. Still, systems with multiple right-hand sides are ubiquitous,
e.g., in tomography~\cite{tournier2016micro} or data
analytics~\cite{KALANTZIS2018136}. Of course, it is possible to cast a system
with multiple right-hand sides into a sequence of systems with the same
coefficient matrix but changing right-hand sides $A x_i = b_i, i =
1,2,\ldots,k$. However, block Krylov methods, at the cost of higher arithmetic
intensities, generate larger subspaces and typically converge in fewer iterates.
There is none implemented in PETSc. It is nevertheless possible to solve
systems with multiple right-hand sides using a specialized type of matrices,
but with a very limited choice of preconditioners, cf.~\cref{sec:matkaij}.
In the context of optimization, it is also
frequent to solve a sequence of linear systems $A_i X_i = B_i, i = 1, 2,
\ldots$

@@

this paragraph is to explain how the results have been reproduced in PETSc.
Thanks to \pk{KSPHPDDM}, it is quite straightforward. First, the sequence of
MATLAB systems had to be converted to PETSc \pk{Mat} and \pk{Vec}. Then, it is
just a matter of calling \pk{KSPSolve} in sequence. The dataset and the source
code are available at

@@

\pk{PCICC} and ichol from MATLAB are not consistent. All PETSc tests are run on four MPI

@@

originally set to $10^{-10}$ are gathered in~\cref{fig:comparison}. Apart from

@@

The Poisson equation on a cube is discretized with $\mathbb{P}_1$ finite elements in double precision. This yields a matrix $A$ of dimension one million. Though the numerical values of $A$ are of no interest here, the sparsity pattern is rather common and frequently encountered, e.g., when discretizing partial differential equations. Then, a random dense matrix $T$ of dimension $b$ is generated, for $b \in \{ 1,3,6 \}$, and the following matrix is evaluated $\mathbb{A} = A \otimes T$. The matrix $\mathbb{A}$ is then assembled into all three formats described above. For block matrices, a block size of $b$ is used. The performance of the \pk{MatProductNumeric} operation is evaluated for tall-and-skinny dense matrices with a varying number of columns $N \in \{1,2,8,16,32,64\}$. For $N=1$, the \pk{MatMult} operation for matrix--vector multiplication is used instead. All results are gathered in~\cref{fig:perfAX}. They can be reproduced using the following mini-app: \url{http://jolivet.perso.enseeiht.fr/MatProduct.cpp} and any input \pk{MatAIJ} stored in binary format, here using the default name binaryoutput.

@@

The physical domain $\Omega$ is a beam of dimensions $[0,6] \times [0,1] \times [0,1]$. It is decomposed in $13{,}824$ subdomains using the automatic graph partitioner ParMETIS~\cite{karypis1998fast}.

@@

@@

By default, the coarse problem in \pk{PCHPDDM} is solved using an exact $LU$ or Cholesky factorization, in this case using 24 processes and MKL CPARDISO. Thanks to the flexibility of PETSc, switching to an inexact solver using \pk{PCHYPRE} (resp.~GenEO multilevel extension), cf.~\cref{enum:inexacthypre} (resp.~\cref{enum:inexact}), is straightforward. \\[-4pt]

>>>>

% Recycling put aside, 
Another important aspect of Krylov methods is their ability
to deal with multiple right-hand sides simultaneously. Block Krylov methods~\cite{gutknecht2006block} are
designed for solving linear systems $A X = B$, where
$X$ and $B$ are tall-and-skinny matrices with $k \geq 1$ columns. These methods are
less frequently implemented in general purpose libraries because they require
somehow more involved kernels such as matrix--matrix multiplication, instead of
matrix--vector. Still, systems with multiple right-hand sides are ubiquitous,
e.g., in tomography~\cite{tournier2016micro} or data
analytics~\cite{KALANTZIS2018136}. % Of course, it is possible to cast a system with multiple right-hand sides into a sequence of systems with the same coefficient matrix but changing right-hand sides $A x_i = b_i, i = 1,2,\ldots,k$. However, 
Block Krylov methods, while having higher arithmetic
intensities, generate larger subspaces and typically converge in fewer iterates.
There is none implemented in PETSc. It is nevertheless possible to solve
systems with multiple right-hand sides using a specialized type of matrices,
but with a very limited choice of preconditioners, cf.~\cref{sec:matkaij}.
In the context of optimization, it is also
frequent to solve a sequence of linear systems $A_i X_i = B_i, i = 1, 2,
\ldots$

@@

this paragraph is to explain how the results have been reproduced in PETSc. % Thanks to \pk{KSPHPDDM}, it is quite straightforward. First, the sequence of MATLAB systems had to be converted to PETSc \pk{Mat} and \pk{Vec}. Then, it is just a matter of calling \pk{KSPSolve} in sequence.
The dataset and the source code are available at

@@

All PETSc tests are run on four MPI

@@

originally set to $10^{-10}$ are gathered in~\cref{fig:comparison}. 
\pk{PCICC} and ichol from MATLAB are not consistent.  Apart from

@@

The Poisson equation on a cube is discretized with $\mathbb{P}_1$ finite elements in double precision. This yields a matrix $A$ of dimension one million. Though the numerical values of $A$ are of no interest here, the sparsity pattern is rather common and frequently encountered, e.g., when discretizing partial differential equations. Then, a random symmetric dense matrix $T$ of dimension $b$ is generated, for $b \in \{ 1,3,6 \}$, and the following matrix is evaluated $\mathbb{A} = A \otimes T$. The matrix $\mathbb{A}$ is then assembled into all three formats described above. For block matrices, a block size of $b$ is used. The performance of the \pk{MatProductNumeric} operation is evaluated for tall-and-skinny dense matrices with a varying number of columns $N \in \{1,2,8,16,32,64\}$. For $N=1$, the \pk{MatMult} operation for matrix--vector multiplication is used instead. All results are gathered in~\cref{fig:perfAX}. They can be reproduced using the following mini-app: \url{http://jolivet.perso.enseeiht.fr/MatProduct.cpp} and any input \pk{MatAIJ} stored in binary format, here using the default name binaryoutput.

@@

The physical domain $\Omega$ is a beam of dimensions $[0,6] \times [0,1] \times [0,1]$.

@@

The physical domain $\Omega$ is decomposed in $13{,}824$ subdomains using the automatic graph partitioner ParMETIS~\cite{karypis1998fast}.

@@

By default, the coarse problem in \pk{PCHPDDM} is solved using an exact $LU$ or Cholesky factorization, in this case using 24 processes and MKL CPARDISO. Switching to an inexact solver using \pk{PCHYPRE} (resp.~GenEO multilevel extension), cf.~\cref{enum:inexacthypre} (resp.~\cref{enum:inexact}), is straightforward. \\[-4pt]
